Cheat Sheet for PFPL

### 2016-08-05 pfpl/draftcheatsheet.tex
Bring up to date

\subsubsection*{32 Fluid Binding}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

@@

>>>>

\subsubsection*{32 Fluid Binding}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\
78 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Tensor product & Tensor product &  Map symbol $a$ to expression $e$\\
79 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Tensor product & Tensor product &  Symbol $a$ is undefined\\
80 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Tensor product & Tensor product &  Symbol $a$ is indeterminate\\

@@

81 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
\end{tabular}
